The role of viscosity on drop impact forces

### 2024-08-27 Rebuttal.R2/Response to Reviewer 2.tex

	\item[$\bullet$] \textit{2. I appreciate the clarification regarding the error bars. However, a proper characterization (and description of the procedure by which they are determined) of the estimated parametric errors is still incomplete. Rather than including additional discussion, the authors reference the supplementary materials of a prior work (Zhang et al. (2022)). In reviewing this work, I cannot identify error assessments on key parameters (such as impact velocity). An error is now included on the droplet size, but there is no discussion of how drop size is determined nor how this error determined. Additionally, the related point regarding horizontal error bars was not addressed. Given that there is no length limit, I would suggest the authors include all details in the present manuscript rather than referring to incomplete discussions in prior work. (Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}\\[2mm]

	We appreciate the reviewer's insistence on a comprehensive error characterization. We have addressed this concern by adding a new appendix to the manuscript, titled ``Note on the experimental error characterization". We have also modified the caption of figure~2 of the main text (see figure~\ref{fig:summary}).

	\oo
	Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~A for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.

	\section*{Appendix A. Note on the experimental error characterization}
	\label{app:error}

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat: Extend discussion on the role of gravity in drop impact
This commit extends the discussion on the role of gravity in drop impact. The
key changes are:

1. Added a new paragraph in Section 2 that discusses the Bond number (Bo) and
   Froude number (Fr) for the system, highlighting that gravity is sub-dominant
   compared to inertia throughout the manuscript (Fr > 1).
2. Removed the dedicated Appendix A on the role of gravity, as the key points
   are now incorporated in the main text.

The motivation for these changes is to provide a more comprehensive
understanding of the system's dimens

In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate. For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}. 
The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle. Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated. Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}). The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. \Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript. In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity. Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
All experiments are conducted at ambient pressure and temperature. The impact force is directly measured using a high-precision piezoelectric force transducer (Kistler 9215A) with a resolution of $0.5\,\si{\milli\newton}$. During these measurements, the high-frequency vibrations induced by the measurement system and the surrounding noise are spectrally removed using a low pass filter with a cut-off frequency of $5\,\si{\kilo\hertz}$, following the procedure in \citet{Li2014, Zhang2017, Gordillo2018, Mitchell2019}. 
The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$. \Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}

@@

We leverage the axial symmetry of the drop impact (figure~\ref{fig:schematic}a). This axial symmetry breaks at large $We$ ($\ge 100$ for water drops and even larger Weber number for more viscous drops), owing to destabilization by the surrounding gas after splashing \citep{xu2005drop, Eggers2010, Driscoll2011, riboux2014experiments, Josserand2016, zhang2022impact}. 
To solve the governing equations~\eqref{eqn:continuity}--\eqref{eqn:VoF}, the velocity field $\boldsymbol{v}$ and time $t$ are normalized by the inertio-capillary scales, $V_\gamma = \sqrt{\gamma/\rho_dD_0}$ and $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$, respectively. Furthermore, the pressure is normalized using the capillary pressure scale $p_\gamma = \gamma/D_0$. In such a conceptualization, $Oh$ and $We$ described in \S\ref{sec:intro} uniquely determine the system. 
The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces. 
The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air. The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). At $t = 0$, in our simulations, we release \Rev{a spherical drop (see appendix~\ref{app:shape})} whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.

>>>>

In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate. For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}. 
The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle. Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated. Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}). The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. 
All experiments are conducted at ambient pressure and temperature. The impact force is directly measured using a high-precision piezoelectric force transducer (Kistler 9215A) with a resolution of $0.5\,\si{\milli\newton}$. During these measurements, the high-frequency vibrations induced by the measurement system and the surrounding noise are spectrally removed using a low pass filter with a cut-off frequency of $5\,\si{\kilo\hertz}$, following the procedure in \citet{Li2014, Zhang2017, Gordillo2018, Mitchell2019}. 
The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$. \Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}

@@

We leverage the axial symmetry of the drop impact (figure~\ref{fig:schematic}a). This axial symmetry breaks at large $We$ ($\ge 100$ for water drops and even larger Weber number for more viscous drops), owing to destabilization by the surrounding gas after splashing \citep{xu2005drop, Eggers2010, Driscoll2011, riboux2014experiments, Josserand2016, zhang2022impact}. 
To solve the governing equations~\eqref{eqn:continuity}--\eqref{eqn:VoF}, the velocity field $\boldsymbol{v}$ and time $t$ are normalized by the inertio-capillary scales, $V_\gamma = \sqrt{\gamma/\rho_dD_0}$ and $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$, respectively. Furthermore, the pressure is normalized using the capillary pressure scale $p_\gamma = \gamma/D_0$. In such a conceptualization, $Oh$ and $We$ described in \S\ref{sec:intro} uniquely determine the system. 
The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces. 
\Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript. In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity. Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air. The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). At $t = 0$, in our simulations, we release \Rev{a spherical drop (see appendix~\ref{app:shape})} whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.
